Results

### 2018-07-16 02_analysis.Rmd
Minor edits + summary of hypotheses

# Session info

>>>>

# Session info
# Summary of hypotheses

```{r hypotheses-summary, warning=FALSE, message=FALSE, results="asis"}
# TODO: Make this more dynamic so I don't have to type all the values manually
hypotheses <- read_csv(here("text", "hypotheses-summary.csv"))

hypotheses %>% 
  pandoc.table.return(justify = "ll", style = "grid", keep.line.breaks = TRUE,
                      caption = "Summary of all hypotheses {#tbl:hypotheses}") %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-hypotheses.md"))
```
